Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-01-31 hscc2017/paper.tex
updated description of benchmarks for HSCC 2017 paper

The first set of benchmarks uses the discrete plant of a cruise control
model for a car, and accounts for rolling friction, aerodynamic drag, and
the gravitational disturbance force~\cite{Astrom08}. The plant model is
given as follows:
%
\begin{equation}
\label{cruise-control-c1}
G_1(z)=\frac{0.0264}{z-0.998} \nonumber
\end{equation}

%Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
%for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
%which has the following mathematical model
%
%\begin{equation}
%\label{cruise-control-g1}
%C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
%\end{equation} 
%
%\begin{equation}
%\label{cruise-control-g2}
%C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
%\end{equation}

The second set of benchmarks considers a simple spring-mass 
damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where the discrete 
plant dynamics is represented by the following $z$-expression:
%
%where both discrete 
%plant dynamics and controller are represented by the following 
%z-expression, resp.
%
\begin{equation}
\label{spring-mass-damper-g}
G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}. \nonumber
\end{equation} 
%
%\begin{equation}
%\label{spring-mass-damper-c}
%C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
%\end{equation}

A third set of benchmarks uses a physical plant for satellite
applications~\cite{Franklin15}.  Satellites require attitude (pose) control
for orientation of antennas and sensors w.r.t.~earth.  The satellite
attitude control is typically used for three-axis attitude tracking, but
here we consider only one axis at a time.  The motion equation for the
one-axis system, disregarding disturbance torques, is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C}, 
\end{equation}
%
\noindent where $I$ is the satellite inertia moment about its mass
center, $\tau_{C}$ is the control torque applied by the thrusters, and
$\theta$ is the controlled attitude angle.  Normalizing
Eq.~\eqref{eq:satelliteode} by defining the control signal
$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
$s$-domain transfer function $G(s)$ is obtained:
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}
%
\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
we get the following $z$-domain model:
%
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
\end{equation}

%The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
%are represented by the following z-expression:
%
%\begin{equation}
%\label{satellite-b2}
%C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
%\end{equation} 
%
%\begin{equation}
%\label{satellite-c2}
%C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
%\end{equation}

The fourth (and last) set of benchmarks considers the following description
for the plant $G_{4}(s)$, which is typically used for evaluating stability
margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}:
%
\begin{equation}
\label{exampleA}
G_{4}(s)=\frac{s-1}{s^{2}-s-2},
\end{equation}
%
\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
and $0.03$ seconds), respectively, as follows:
%
\begin{equation}
\label{exampleA-sampletime1}
G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime2}
G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime3}
G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
\end{equation}

>>>>

The first set of benchmarks uses the discrete plant $G_1(z)$ of a cruise control
model for a car, and accounts for rolling friction, aerodynamic drag, and
the gravitational disturbance force~\cite{Astrom08}. 
%The plant model is given as follows:
%
%\begin{equation}
%\label{cruise-control-c1}
%G_1(z)=\frac{0.0264}{z-0.998} \nonumber
%\end{equation} 
%
The second set of benchmarks considers the discrete plant $G_2(z)$ 
of a simple spring-mass damper~\cite{DBLP:conf/hybrid/WangGRJF16}. 
%where the discrete 
%plant dynamics is represented by the following $z$-expression:
%
%\begin{equation}
%\label{spring-mass-damper-g}
%G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}. \nonumber
%\end{equation} 
%
A third set of benchmarks uses the discrete plant $G_{3}(z)$ for satellite
applications~\cite{Franklin15}.  Satellites require attitude (pose) control
for orientation of antennas and sensors w.r.t.~earth.  The satellite
attitude control is typically used for three-axis attitude tracking, but
here we consider only one axis at a time.  
%The motion equation for the
%one-axis system, disregarding disturbance torques, is given by
%
%\begin{equation}
%\label{eq:satelliteode}
%I\cdot \ddot{\theta} = \tau_{C}, 
%\end{equation}
%
%\noindent where $I$ is the satellite inertia moment about its mass
%center, $\tau_{C}$ is the control torque applied by the thrusters, and
%$\theta$ is the controlled attitude angle.  Normalizing
%Eq.~\eqref{eq:satelliteode} by defining the control signal
%$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
%$s$-domain transfer function $G(s)$ is obtained:
%
%\begin{equation}
%\label{eq:satellitetf}
%G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
%\end{equation}
%
%\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
%we get the following $z$-domain model:
%
%\begin{equation}
%G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
%\end{equation}
%
The fourth set of benchmarks considers the discrete plant $G_{4}(z)$
that is typically used for evaluating stability
margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
%
%\begin{equation}
%\label{exampleA}
%G_{4}(s)=\frac{s-1}{s^{2}-s-2},
%\end{equation}
%
%\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
%in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
%and $0.03$ seconds), respectively, as follows:
%
%\begin{equation}
%\label{exampleA-sampletime1}
%G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
%\end{equation}
%
%
%\begin{equation}
%\label{exampleA-sampletime2}
%G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
%\end{equation}
%
%\begin{equation}
%\label{exampleA-sampletime3}
%G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
%\end{equation}

The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete plant $G_{5}(z)$, which 
describes the angular velocity of a DC Motor~\cite{Franklin15}. 
%
%\begin{equation}
%\label{DC-Motor-Rate}
%G_{5}(z)=\frac{ 0.1898z + 1.8027\times{10^{-4}}}{1.0z^{2} -0.9012z -1.0006\times{10^{-16}}}. \nonumber
%\end{equation}
%
The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete plant $G_{6}(z)$,
which provides the longitudinal motion model of a helicopter~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Helicopter-Longitudinal-Motion}
%G_{6}(z)=\frac{15.1315z^{2} + 17.8600z + 17.4549}{z^{3} -2.6207z^{2} + 2.3586z -0.6570}. \nonumber
%\end{equation}
%
The seventh set of benchmarks contains the \textit{Inverted Pendulum} discrete plant $G_{7}(z)$, which 
describes a pendulum model with its center of mass above its pivot point~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Inverted-Pendulum}
%G_{7}(z)=\frac{0.0263z^{2} + 0.0143z -0.0383}{z^{4} -4.2553z^{3} + 6.5105z^{2} -4.2553z + 1}. \nonumber
%\end{equation}
%
The eighth set of benchmarks contains the \textit{Magnetic Suspension} discrete plant $G_{8}(z)$,
which provides a model for which a given object is suspended via magnetic field~\cite{Franklin15}. 
%
%\begin{equation}
%\label{Magnetic-Suspension}
%G_{8}(z)=\frac{6.769\times{10^{13}}z + 6.784\times{10^{13}}}{z^{2} -5.415\times{10^{13}}z + 4.23\times{10^{11}}}. \nonumber
%\end{equation}

The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete plant $G_{9}(z)$,
which presents a model that connects a car to its wheels and allows relative motion between both parts~\cite{Franklin15}.
%
%\begin{equation}
%\label{Car-Suspension}
%G_{8}(z)=\frac{0.25z^{3} + 0.5z^{3} + 0.25z -5.7065\times{10^{-10}}}{z^{3} + 6.8455\times{10^{-9}}z^{2} + 3.3925\times{10^{-17}}z - 3.4667\times%{10^{-94}}}. \nonumber
%\end{equation}
%
The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete plant $G_{10}(z)$, which 
describes a system to read and write data on a storage device in the computer~\cite{Franklin15}.
%
%\begin{equation}
%\label{Computer-Tape-Driver}
%G_{10}(z)=\frac{0.0200z -3.8303\times{10^{-176}}}{1.0z -4.6764\times{10^{-166}}}. \nonumber
%\end{equation}
The last two set of benchmarks describe discrete plants $G_{11}(z)$ and $G_{12}(z)$ 
for a DC servo motor application (e.g., velocity control)~\cite{exampleCAD,Tan01}.
